How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-28 tse-paper/content.tex
Review until page 6

\subsubsection{What information is targeted in build logs? (RQ 1.1)}

\begin{figure}
\centering
\begin{subfigure}[t]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/info_target.pdf}
		\caption{Information targeted in build log analysis.}
		\label{fig:litsur:info_target}

@@

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
\Cref{fig:litsur:log_producer} shows the distribution of supported
build tools.
Of the articles we surveyed, 30\% analyzed
Maven~\cite{maven2019website} build logs,
16\% analyzed Gradle~\cite{gradle2020website} logs
and 10\% analyzed Ant~\cite{ant2020website} logs.

A large amount of the articles within the survey, analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs changes
~\cite{staahl2014modeling} and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
% remove following part of this paragraph?
% I think it is a nice anecdote but not super necessary yes.
Sometimes, aspects separate from the build log analysis motivate
their limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.

Only 7\% of the proposed methods claimed to be language-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) targeted logs from a source that no
second article
targeted.

In 38\% of cases, the articles collected build logs from Travis
CI~\cite{travisci2019webpage}.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

% perhaps remove this paragraph?
% C: made it more specific, this is the only reference in the result
% which supports 'we need automatic because so many logs are analy'
The number of logs analyzed varied greatly between the articles
and we were not always able to
extract it confidently.
23 of the articles analyzed more than a thousand build logs, some
investigated up to 122 million logs.

31\% of the surveyed articles claimed to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other articles studied.

% TODO Caro: adapt as discussed
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

\textbf{TODO embed custom plugin discussion}
% TODO very disconnected here
From this, we follow: 1) there is a niche for custom parsers or even
specialized plugins integrated into the build process to make
post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
%TODO cite
wrote, have the disadvantage of not being able to work on historic
builds.
2) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
%TODO here we sell our techniques as superior.
% match in intro?
%TODO: really? currently the discussion does not show this 'need'!
The outcome of our literature survey shows the need for a new
generation of techniques to analyze build logs.
In this section we argue how our research sets the first step to
address this need by introducing three techniques that retrieve
specific substrings (chunks) from build logs.
We present defining characteristics of these so called \emph{chunk
retrieval techniques} and present the techniques we developed in
detail.
At the end we illustrate how the techniques operate on a concrete
example and sketch out their implementation.

@@

\subsection{The Case for Chunk Retrieval on Build Logs}
In summary, the results of the literature study show the need for
build log
analysis techniques that are \emph{automated},
\emph{build-environment agnostic}
and can be \emph{configured with little effort}.

% what we need is some derivation of the three techniques 1) regex 2)
%cts 3) kws, best repeated here in the discussion and then from the lit
%survey above, section 2.4.2
For this reason, we are focussing on techniques that run automatically
after being configured through examples or keywords.
\emph{Examples consist of logs and corresponding chunks.}
The user provides these examples and keywords, which can simply be
exchanged whenever new cases are introduced.

@@

We implement three chunk retrieval techniques based on approaches
previously described by several articles:
PBE mimics regular expressions and parsers while simplifying
their development.
We chose text similarity (CTS) as a common information retrieval
technique and implement the ad-hoc approach of
searching for specific strings or keywords within KWS\@.

To evaluate and compare the three chunk retrieval techniques
we create a data set with logs from failed builds and corresponding
chunks that describe error messages or
``the reason the build failed.''
This was also the information
most targeted by the articles in our survey
In addition to that, our data set encompasses a broad range of
build environments which enables us to measure the generic
applicability of the techniques.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
Next, we will present our definition of chunk retrieval techniques
which automatically
retrieve pieces of information that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.
% and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

>>>>

\subsubsection{What information is targeted in build logs? (RQ 1.1)}
\label{sec:rq11}
\begin{figure}
\centering
\begin{subfigure}[t]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/info_target.pdf}
		\caption{Information targeted in build log analysis.}
		\label{fig:litsur:info_target}

@@

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}, and
another two 
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
\Cref{fig:litsur:log_producer} shows the distribution of supported
build tools.
Of the articles we surveyed, 30\% analyzed
Mave~\cite{maven2019website},
16\% analyzed Gradle~\cite{gradle2020website},
and 10\% analyzed Ant build logs~\cite{ant2020website}.

A large amount of the articles analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs changes
~\cite{staahl2014modeling} and
therefore \textbf{``parsers must be specialized to each build and test
framework''}~\cite{tomassi2019bugswarm}.
Sometimes, aspects separate from the build log analysis motivate
the limitation to a specific build tool.
For example, Shi et al. focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score~\cite{shi2018evaluating}. PIT is only available as a Maven plugin.

Only 7\% of the proposed methods claimed to be language-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) used logs from a source that no
second article
targeted.
In 38\% of cases, the articles collected build logs from Travis
CI~\cite{travisci2019webpage};
18\% of the articles processed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the articles
and we were not always able to
extract it confidently.
23 of the articles analyzed more than a thousand build logs, some
investigated up to 122 million logs.
Of the surveyed articles, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other articles studied.

% TODO Caro: adapt as discussed
% TODO: I think the axes labels are also unncessary for this graph.
%Our other graphs in the lit survey do not have them, either.
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

\textbf{TODO embed custom plugin discussion}
% TODO very disconnected here
From this, we follow: 1) there is a niche for custom parsers or even
specialized plugins integrated into the build process to make
post-factum
parsing of logs redundant. Their advantage is that they can precisely report the information which is required.
A downside of plugins, which are integrated into the CI flow similar to Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable to work on historic
builds, i.e., before the moment they were being deployed and that if information has not been recorded from the beginning but turns out to be important, it is impossible to retrieve later.
2) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
%TODO here we sell our techniques as superior.
% match in intro?
%TODO: really? currently the discussion does not show this 'need'!
The outcome of our literature survey shows the need for a new
generation of techniques to analyze build logs.
In this section we argue how our research sets the first step to
address this need by introducing three techniques that retrieve
specific substrings (chunks) from build logs.
We present defining characteristics of these so called \emph{chunk
retrieval techniques} and present the techniques we developed in
detail.
% TODO At the end of what?
At the end we illustrate how the techniques operate on a concrete
example and sketch out their implementation.

@@

\subsection{The Case for Chunk Retrieval on Build Logs}
In summary, the results of the literature study show the need for
build log
analysis techniques that are \emph{automated},
\emph{agnostic of the build environment}
and can be \emph{configured with little effort}.

% what we need is some derivation of the three techniques 1) regex 2)
%cts 3) kws, best repeated here in the discussion and then from the lit
%survey above, section 2.4.2
For this reason, we are focussing on techniques that run automatically
after being configured through examples or keywords.
\emph{Examples consist of logs and corresponding chunks.}
The user provides these examples and keywords, which are easy to adapt whenever the user adds new examples.

@@

We implement three chunk retrieval techniques based on approaches
previously described by several articles:
PBE mimics regular expressions, while simplifying
their development.
We chose text similarity (CTS) as a common information retrieval
technique and implement the ad-hoc approach of
searching for specific strings or keywords within KWS\@.

To evaluate and compare the three chunk retrieval techniques
we create a data set with logs from failed builds and corresponding
chunks that describe error messages or
``the reason the build failed.''
This was also the information
most targeted by the articles in our survey (see \Cref{sec:rq11}).
In addition to that, our data set encompasses a broad range of
build environments which enables us to measure the generic
applicability of the techniques.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
% TODO Caro: Wouldn't this place perhaps be better to contain
%the pargraph about why chunk log techniques are more general
% than other approaches?

\label{sec:crt-characteristics}
In this section, we formalize our use of chunk retrieval techniques. By this word, we refer to techniques that automatically
retrieve pieces of information that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.
% and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.
